---
title: "Sample DataViz Portfolio"
---

Add/Edit more contents [as you wish!]{.underline}

## Data Visualizations

Generate Example graphs using the penguins data from `palmerpenguins` using `R` and `GGPlot2`

## **About the data**

Data were collected and made available by [Dr. Kristen Gorman](https://www.uaf.edu/cfos/people/faculty/detail/kristen-gorman.php) and the [Palmer Station, Antarctica LTER](https://pallter.marine.rutgers.edu/), a member of the [Long Term Ecological Research Network](https://lternet.edu/).

## **Installation**

You can install the released version of palmerpenguins from [CRAN](https://cran.r-project.org/) with:

```         
install.packages("palmerpenguins")
```

To install the development version from [GitHub](https://github.com/) use:

```         
install.packages("remotes") 
remotes::install_github("allisonhorst/palmerpenguins")
OR
remotes::install_github("mohitshrestha/automaton")
```

```{r}
#| echo: true
#| message: false
#| warning: false
#| code-fold: true

# To install the released version from CRAN use:
# install.packages("ggplot2")
# install.packages("palmerpenguins")

# To install the development version from GitHub use:
# install.packages("remotes")
# remotes::install_github("allisonhorst/palmerpenguins")
# remotes::install_github("mohitshrestha/automaton")

library(ggplot2)
library(palmerpenguins)
ggplot2::theme_set(ggplot2::theme_minimal())
```

## Generate Visualizations

### Penguin Bill Length versus Flipper Length

```{r}
#| echo: true
#| message: false
#| warning: false
#| code-fold: true

flipper_len_bill_len <- ggplot(data = penguins,
                         aes(x = flipper_length_mm,
                             y = bill_length_mm,
                             group = species)) +
  geom_point(aes(color = species, 
                 shape = species),
             size = 3,
             alpha = 0.8) +
  geom_smooth(method = "lm", se = FALSE, aes(color = species)) +
  scale_color_manual(values = c("darkorange","purple","cyan4")) +
  labs(title = "Penguin Bill Length versus Flipper Length",
       subtitle = "Dimensions for Adelie, Chinstrap and Gentoo Penguins at Palmer Station LTER",
       x = "Flipper length (mm)",
       y = "Bill length (mm)",
       color = "Penguin species",
       shape = "Penguin species") +
  theme(legend.position = c(0.85, 0.15),
        plot.title.position = "plot",
        plot.caption = element_text(hjust = 0, face= "italic"),
        plot.caption.position = "plot")

flipper_len_bill_len
```

### Penguin Body Mass versus Flipper Length

```{r}
#| echo: true
#| message: false
#| warning: false
#| code-fold: true

ggplot(penguins, aes(x = flipper_length_mm,
                            y = body_mass_g)) +
  geom_point(aes(color = sex)) +
  scale_color_manual(values = c("darkorange","cyan4"), na.translate = FALSE) +
  labs(title = "Penguin Body Mass versus Flipper Length",
       subtitle = "Dimensions for male and female Adelie, Chinstrap and Gentoo Penguins at Palmer Station LTER",
       x = "Flipper length (mm)",
       y = "Body mass (g)",
       color = "Penguin sex") +
  theme(legend.position = "bottom",
        plot.title.position = "plot",
        plot.caption = element_text(hjust = 0, face= "italic"),
        plot.caption.position = "plot") +
  facet_wrap(~species)
```

## Citation
```{r}
#| echo: true
#| message: false
#| warning: false
#| code-fold: true

citation("palmerpenguins")
```

